Blocking-resistant communication\\through domain fronting

### 2014-07-08 docs/meek.tex
Put "domain fronting" in the title.
Use IEEE style.
Line break in title.
Nobody will care about the Heartbleed gap.

\documentclass{article}  
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}

@@

\title{Blocking-resistant communication through high-value web services}
\author{David Fifield, Chang Lan}

@@

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
The gap between April~14 and April~22 is when the Tor bridge authority
was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
\label{fig:clients}
\end{figure}

@@

\section{Acknowledgments}

@@

\bibliographystyle{plain}  
\bibliography{meek}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}

@@

@@

\title{Blocking-resistant communication\\through domain fronting}

\author{David Fifield, Chang Lan}
\author{
\IEEEauthorblockN{David Fifield and Chang Lan}
\IEEEauthorblockA{University of California, Berkeley}
}

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.}
\label{fig:clients}
\end{figure}

@@

\section*{Acknowledgments}

@@

\bibliographystyle{IEEEtran}
\bibliography{meek}
